An assessment of photometric redshift PDF performance in the context of LSST

### 2018-08-20 paper/main.tex

%\documentclass[a4paper]{article}
\documentclass[usenatbib]{mn2e}
%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\linenumbers
\modulolinenumbers[2]

\usepackage{natbib}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{multirow}

\newcommand       \apj  {ApJ}
\newcommand       \apjl  {ApJL}
\newcommand       \apjs  {ApJS}
\newcommand       \aj  {AJ}
\newcommand       \aap {A\&A}
\newcommand       \mnras {MNRAS}
\newcommand       \nat {Nature}
\newcommand       \araa {ARA\&A}
\newcommand       \physrep {Phys.~Reports}
\newcommand       \prd {Phys. Rev. D}

@@

\def\X{{\mathbf{X}}}
\def\x{{\mathbf{x}}}
\def\E{{\mathbb E}}

\title{An assessment of photometric redshift PDF performance in the context of LSST}
% Alternate title proposal: Assessing the characterization of photometric redshift uncertainties in the regime of LSST

\author{LSST-DESC Photometric Redshift Working Group}

\begin{document}
\maketitle

\begin{abstract}
Photometric redshift (photo-$z$) probability distribution functions (PDFs) are a key data product of nearly all upcoming galaxy imaging surveys.
However, the photo-$z$ PDFs resulting from different techniques are not in general consistent with one another, and an optimal method for obtaining an accurate PDF remains unclear.  
We present the results of an initial study of the Large Synoptic Survey Telescope Dark Energy Science Collaboration (LSST-DESC), the first in a planned series of papers testing multiple photo-$z$ codes on simulations of upcoming LSST galaxy photometry catalogues.  This initial test evaluates photo-$z$ algorithms in the presence of representative training data and in the absence of several common sources of systematic errors that affect the procedures by which photo-$z$ PDFs are derived.  
The photo-$z$ PDFs are evaluated using multiple metrics including the Kolmogorov-Smirnoff statistic, Cramer-von Mises statistic, Anderson-Darling statistic, Kullback-Leibler divergence, $N(z)$ moments, quantile-quantile plots and probability integral transform.  We observe several trends, including an overall over/under-prediction in the broadness of the PDFs for several of the codes.  A careful accounting of all systematics discovered will be necessary for the codes employed in upcoming analyses in order to achieve unbiased cosmological measurements.
\end{abstract}
\begin{keywords}
galaxies: distances and redshifts -- galaxies: statistics -- methods: statistical
\end{keywords}
%\noindent comments color-code:\\
%\red{SJS},
%\aim{AIM},
%\scc{SC},
%\textcolor{brown}{MB},\jan{JAN}
%\blue{unknown}\\
%\red{note: not all red text is mine, at some point various people were using red --SJS.}

% Questions left unanswered:
% 1. Which journal will this paper be published? 
% Answer: AJ / ApJ / MNRAS (no charges, but not sure if it will accept a paper based on a DC1 effort and the associated simulations)
% 2. What is the meaning of $p(z)$ in different codes? (Ofer)
% Answer: ?
%

\section{Introduction}
\label{sec:intro}

%(Sam Schmidt, Ofer Lahav, Jeff Newman, Alex Malz, John Soo, Tony Tyson)

%\jan{Is the intention to keep these parenthetical author sets?  I find it a bit offputting in the text.  It might be better to put this for sections in the acknowledgements section, and for individual codes/statistics specify who ran/developed it with a sentence.}\red{I was just about to comment these out before finalizing the internal review draft of the paper. They are in place to remind me to contact a few people who still have not filled out their authors.csv info.}

Large-scale photometric galaxy surveys are entering a new era with currently or soon-to-be running Stage III and Stage IV dark energy experiments like the Dark Energy Survey \citep[DES,][]{Abbott:05}, the Kilo-Degree Survey \citep[KiDS,][]{de_Jong:13}, Large Synoptic Survey Telescope \citep[LSST,][]{Abell:09}, Euclid \citep{Laureijs:11}, and Wide-Field Infrared Survey Telescope \citep[WFIRST,][]{Green:12}. 
The move to imaging based surveys, rather than spectroscopic based, for cosmological measurements makes proper understanding of photometric redshifts (``photo-$z$'s'') of paramount importance, as cosmological distance measures for statistical samples are directly dependent on photo-$z$ measurements.

The unprecedented sample size of LSST galaxies, expected to number several billion for the main cosmological sample, necessitates stringent constraints on photo-$z$ accuracy if systematic errors are not to dominate the statistical errors. 
The LSST Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} lists the photometric redshift goals for a magnitude limited sample with $i<25$ as: root-mean-square error with a goal of $\sigma_z<0.02(1+z)$; $3\sigma$ ``catastrophic outlier'' rate below $10\%$; bias below $0.003$\footnote{ 
Note that at the time the SRD was written, these goals were stated in terms of a photo-$z$ point estimate for each galaxy, as was standard in many previous studies, while in this paper we emphasize the importance of using a full photo-$z$ PDF.}.

The tremendous size of LSST's galaxy catalog will be enabled by its exceptional depth, pushing to fainter magnitudes and deeper imaging and including galaxies of lower luminosity and higher redshift than ever before. 
In addition to the contribution of low signal-to-noise photometry to the systematic error of photo-$z$s, these populations introduce major physical degeneracies, for example the Lyman break/Balmer break degeneracy, that were not present in the populations covered in previous large area surveys like the Sloan Digital Sky Survey \citep[SDSS,][]{York:00} and the Two Micron All Sky Survey \citep[2MASS,][]{Skrutskie:06}.  In order to meet LSST's demanding error budget, it will be necessary to fully characterize those degeneracies wherein multiple redshift solutions have comparable likelihood.

There is often a desire to have a single valued ``point-estimate'' redshift for an individual galaxy.  However, the complex, non-linear (and often non-unique) nature of the mapping between broad band fluxes and redshift means that a single value is unable to capture the full redshift information encoded in a galaxy's magnitudes.  For example, a common point-estimate for a template-based method is taking the highest likelihood solution as the point photo-$z$.  A single valued redshift ignores degenerate redshift solutions of lower probability, potentially biasing photometric redshift estimates both for individual galaxies and ensemble distributions.  Storing more information is necessary, most often photo-$z$ codes output the redshift probability density function (PDF), also often referred to as $p(z)$, describing the relative likelihood as a function of redshift. %\red{should we move some of AIM's p(z) vs p(z|d,I) to here?}
Early template methods such as \citet{Fernandezsoto:99} converted relative $\chi^2$ values of template spectra to likelihoods to estimate $p(z)$.  Soon after, codes such as \citet{Benitez:00} added a Bayesian prior and output a posterior probability distribution.  While many early machine learning based algorithms focused on a point-estimate, \citet{Firth:03} used a neural net with 1000 realizations scattered within the photometric errors to estimate a $p(z)$. 
As more groups began to employ photometric redshifts in their cosmological analyses, realization that point-estimate photo-$z$'s were inadequate for precision cosmology measurements \citep{Mandelbaum:2008}.  From around this point onward, most photo-$z$ algorithms have attempted to implement some estimate of the overall redshift probability in their outputs, and some surveys began supplying a full $p(z)$ rather than a simple redshift point-estimate and error \citep[e.~g.~][]{de_Jong:17}.

%\aim{We should spend a whole paragraph establishing that photo-$z$ PDFs are a thing, i.e. review the motivation for PDFs over point estimates, basic definition, early methods papers, surveys that have published them, etc.}
%\scc{I agree with Alex, we should introduce here what a pdf is and which survey have already published some pdfs (KiDS dr3 for example) or will produce them (LSST, Euclid etc.)}
%\red{See above paragraph, does this adequately address this?--SJS}\scc{fine for me}

There are numerous techniques for deriving photo-$z$ PDFs from photometry, yet no one method has yet been established as clearly superior.
Quantitative comparisons of photo-$z$ methods have been made before.  
The Photo-$z$ Accuracy And Testing \citep[PHAT,][]{Hildebrandt:10} effort focused on point estimates derived from many photometric bands. 
DES compared several codes for point estimates \citep{Sanchez:14} and a summary statistic of photo-$z$ interim posteriors for tomographically binned galaxy subsamples \citep{Bonnett:16}. 
This paper is distinguished by its inclusion of metrics of photo-$z$ interim posteriors themselves and consideration of both classic and state-of-the-art photo-$z$ algorithms, comparing the performance of several of the most widely employed codes as well as some that have been developed only recently on the basis of metrics appropriate for a probabilistic data product. 
The results presented in this work are 
%part of the Data Challenge 1 (DC1) 
 a major focus of the Photometric Redshift working group of the LSST Dark Energy Science Collaboration (LSST-DESC).  This work is laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}} as one of the critical activities to be completed in preparation for dark energy science analysis on the first year LSST data. 
This is the first of multiple papers by the working group, which will grow in sophistication.
In this initial paper we focus on evaluating the performance of photometric redshift codes and their ability to produce accurate PDFs in the presence of representative training sets.  This can be thought of as an initial test under near perfect conditions, before further complexities are added in future papers.  Comparing the relative performance of the codes enables us to evaluate whether each code is using information in an optimal way, and may reveal enhancements in some codes and deficiencies in others, either in the fundamental algorithm, or in specific implementation.

Certain science cases need redshift information on individual objects, e.~g.~identification of host galaxy redshift for supernova classification, or identifying potential cluster membership.  
Other science cases need only ensemble redshift information; for instance current weak lensing techniques require the overall redshift distribution $N(z)$ for tomographic redshift samples, but do not need single galaxy estimates. 
In the case of the multiple types of probes of cosmology enabled by the
LSST cosmology sample of several billion galaxies, the number of redshift bins and their photo-$z$ requirements vary with the specific probe;  2-point angular correlations benefit from many bins, while weak lensing probes do not (due to the wide lensing kernel).
Large photometric surveys such as LSST must develop algorithms that meet the needs of all such science cases.  
In order to meet these ambitious goals for photo-$z$ accuracy, every aspect of photo-$z$ estimation will have to be optimized: the algorithms employed, both template and machine-learning based (both in design and implementation); the spectroscopic data used as a training set for machine learning algorithms or to estimate template sets and train Bayesian priors; and probabilistic catalog compression schemes that balance information retention against limited storage resources.

Before moving forward, we must address how the best methods may be unique to the performance metrics and science cases considered and what distinguishes photo-$z$ PDFs of different methods from one another.
Though photo-$z$ PDFs are often written simply as $p(z)$, the PDF itself must be an interim posterior distribution $p(z | d, I)$, the probability of redshift conditioned on photometric data $d$ that has actually been observed and the prior information $I$ that guides how a redshift is extracted from the photometry.
If we run multiple photo-$z$ codes on a single dataset, the photo-$z$ interim posteriors will not be identical because each code is based on assumptions in the form of an interim prior --- these assumptions form the premise for photo-$z$ estimation as a whole and are the only way to introduce differences in estimates of what would otherwise be a shared photo-$z$ posterior $p(z | d)$ regardless of the code used to obtain it.
Though explicit knowledge of the interim prior is necessary to use photo-$z$ interim posteriors self-consistently in physical inference, the interim prior of a particular methodology is often implicit and not necessarily shared among all galaxies in the catalog.

This paper therefore aims (1) to constrain the impact of the interim prior $I$ by separating it into a component $I_{H}$ representing the method itself and a component $I_{D}$ representing physical information, such as a training set or SED template library and (2) to present a procedure for evaluating the performance of photo-$z$ codes in generic tests that may include many more systematics in the interim prior $I$.
In order to isolate the effects encapsulated by $I_{H}$ of variation between codes from issues with the training set or template library encapsulated by $I_{D}$, we use an identical set of simulated galaxies for every code and construct a template library and training sample that are {\it complete and representative} and shared among all codes; that is, our training sample for machine learning codes is drawn from the same underlying galaxy population as our test set, with no additional selections, and the SED library used for template-based codes is the same as the one used to generate the photometric data.  
We explore a number of performance metrics in this paper, not to make a conclusion regarding the superiority or even relative favorability of each code but to establish a method for comparing photo-$z$ PDFs derived by different methods.
These test conditions set the stage for addressing in a future paper the crucial issue of incomplete and non-representative prior information.

The outline of the paper is as follows: in \S\,\ref{sec:sims} we present the simulated data set; in \S\,\ref{sec:pzcodes} we describe the current generation codes employed in the paper;  in \S\,\ref{sec:metrics} we discuss the interpretation of photo-$z$ PDFs in terms of metrics of accuracy; in \S\,\ref{sec:results} we show our results and compare the performance of the codes; in \S\,\ref{sec:discussion} we offer our conclusions and discuss future extensions of this work.

\section{The simulation and mock galaxy catalog}
\label{sec:sims}
%(Sam Schmidt, Eve Kovacs, Tina Peters)

In order to test the current generation codes, we employ a simulated galaxy catalogue. The simulation is completely catalogue-based, with no image construction or mock measurements made. We describe these in detail below.

\subsection{Buzzard-v1.0 simulation}
\label{sec:buzzard}
The \textsc{Buzzard-highres-v1.0} \red{put in cites to in prep Buzzard papers} catalogue construction started with a dark matter only simulation. This N-body simulation contained $2048^3$ particles in a $400$ Mpc h$^{-1}$ box. \red{[N]} snapshots (with smoothing and interpolation between snapshots) were saved in order to construct a lightcone. Dark matter halos were identified using the \textsc{Rockstar} software package \citep{Behroozi:13}. These dark matter halos were populated with galaxies with a stellar mass and absolute $r$-band magnitude in the SDSS system determined using a sub-halo abundance matching model constrained to match both projected two-point galaxy clustering statistics and an observed conditional stellar mass function \citep{Reddick:13}.

To assign an SED to each galaxy, the {\it Adding Density Dependent Spectral Energy Distributions} (\textsc{ADDSEDS}, deRose in prep.)\footnote{\url{https://github.com/vipasu/addseds}} procedure was used. This consisted of training an empirical relation between absolute $r$-band magnitude, local galaxy density, and SED using a sample of $\sim 5e^{5}$ galaxies from the magnitude-limited Sloan Digital Sky Survey Data Release 6 Value Added Galaxy Catalog \citep{Blanton:05}\red{[Note: is this the proper reference to SDSS-NYU VAGC? File is called combined\_dr6\_cooper.fits, but I don't see which Cooper et al 2006 this is supposed to refer to?]}. Each SDSS spectrum is fit with a sum of five SED components using the \textsc{k-correct \red{v?}} software package\footnote{\url{http://kcorrect.org}} \citep{Blanton:07}, thus each galaxy SED is parameterized as five weights for the basis SEDs. The distance to the spatial projected fifth-nearest neighbour was used as a proxy for local density in the SDSS training sample. For each simulated galaxy, a ``random'' \red{[details]} galaxy with ``similar'' \red{[details]} absolute $r$-band magnitude and local galaxy density was chosen from the training set, and that training galaxy's SED was assigned to the simulated galaxy. Given the SED, absolute $r$-band magnitude and redshift, we computed apparent magnitudes in the six LSST filter passbands, $ugrizy$. We assigned magnitude errors in the six bands using the simple model described in \citet{Ivezic:08}, assuming full 10-year depth observations had been completed.  The number of total 30-second visits assumed when generating the photometric errors differs slightly from the fiducial numbers assumed for LSST: we assume 60 visits in u-band, 80 visits in g-band, 180 visits in r-band, 180 visits in i-band, 160 visits in z-band, and 160 visits in y-band.
%numbers taken from Alex Abate's photErrorModel.py script in PhotoZDC1 repository, which was used with nYrObs=10.

\subsubsection{Selection of training and test sets}
\label{sec:buzztraining}
The total catalogue covered $400$ square degrees and contained $238$ million galaxies to an apparent magnitude limit of $r\!=\!29$ and spanning the redshift range $0\!<\!z\!\leq\!8.7$. This catalogue contained two orders of magnitude more galaxies than were needed for this study, so only $\sim\!8$ square degrees were used. Systematic problems with galaxy colors above $z\!>\!2$ were observed, so the catalogue was trimmed to include only galaxies in the redshift range $0\!<\!z\!\leq\!2.0$. A random subset of the the remaining galaxies was chosen, and placed at random into either a ``training'' set ($10$ per cent of the sample), for which the galaxies true redshifts will be supplied, or a ``test'' set (the remaining $90$ per cent of the sample), for which each code will need to predict a redshift PDF for each galaxy. The resulting catalogues contain $111\,171$ training galaxies and $1\,000\,883$ test galaxies.  We restrict our analysis to a sample with $i<25.3$, which give a signal-to-noise $\sim\,30$ for most galaxies, a cut often referred to as the expected ``LSST Gold Sample''.  This magnitude cut results in a training set with $44\,404$ galaxies and a test set containing $399\,356$ galaxies.  All subsequent results will evaluate this ``gold sample'' test set.

\subsubsection{Templates}
\label{sec:buzztemplates}
As mentioned in Section~\ref{sec:buzzard}, the SEDs in the Buzzard simulation are drawn from an empirical set of SEDs taken from the SDSS DR6 NYU-VAGC, a sample of roughly $\sim5e^{5}$ galaxies with spectra in SDSS. To determine a finite set of templates to use with template fitting codes we take the five SED weight coefficients for each of the $\sim 500\,000$ galaxies in the SDSS sample and run a simple K-means clustering algorithm on this five dimensional space. The K-means cluster centres span the space of coefficients and properly reflect the underlying density in the coefficient space, thus providing a reasonable approximation for a spanning SED set. An ad-hoc number of $K=100$ was chosen and the $100$ K-means centre positions are taken as the weights for the \textsc{k-correct} SED components to construct one hundred template SEDs. These $100$ templates were provided, 
%\red{(JS: if I remembered correctly, weren't there 150 templates given? Answer: no, initially I supplied a list of 150 that were drawn with a different algorithm, but once we switched to the final k-means set I only supplied 100 (the initial algorithm over-weighted outlier SEDs, which is why we needed the extra 50)--SJS)}
however not every template code uses this set of one hundred templates: because EAZY was designed and written to use the same five basis templates employed by \textsc{k-correct} when constructing our mock galaxies, EAZY was run using linear combinations of these five templates rather than using the 100 discrete templates.

\subsubsection{Limitations}
\label{sec:buzzlimitations}
For our initial investigation of photometric redshift codes, we begin with a data set that is somewhat idealized, and does not contain all of the complicating factors present in real data.  In several cases, the simplification is done with a purpose, with potentially confounding effects excluded in order to better isolate the differences between current-generation photo-$z$ codes, and their causes.  We list several of the simulations limitations in this section.  
As the simulation is catalogue-based, no image level effects, such as photometric measurement effects, object blending, contamination from sky background (Zodiacal light, scattered light, etc...), lensing magnification, or Galactic reddening are included.  No stars are included in the catalogue, nor are the effects of AGN.
As all SEDs are constructed from only five basis templates, properties of the galaxy population will be restricted to follow linear combinations of the characteristics of the five basis templates, so certain non-linear features, for example the full range of emission line fluxes relative to the continuum, will not be included in the model galaxy population.  No additional dust reddening intrinsic to the host galaxy is included, the only approximation of dust extinction comes in the form of dust encoded in the five basis SEDs via the training set used to create the basis templates.  Simple linear combinations of these basis templats will, once again, not explore the full range of realistic dust extinction observed in galaxy populations.

%\subsection{ABC-Galacticus simulation}
%\label{sec:galacticus}
%\red{The Argonne-Berkeley-Carnegie (ABC) Galacticus cosmological simulation uses a semi-analytic model to simulate the galaxy properties and is not directly tuned to observations. Each simulated SED is replaced with a SED drawn from the distribution of empirical SEDs given by the SED Atlas of \citet{Brown:14} (diffusion maps method in development).}

\section{Methods}
\label{sec:pzcodes}

%(Sam Schmidt, Rongpu Zhou, Ibrahim Almosallam, Eric Nuss, Johann Cohen Tanugi, John Soo)

Here we outline the photo-$z$ PDF codes tested in this study. In total, eleven distinct codes are tested.  This sample is not comprehensive, but does cover a broad range of current-generation codes.  Both template-based and machine learning approaches are included and each are described separately in Secs.~\ref{sec:templatecodes} and \ref{sec:trainingcodes} respectively. The list of codes are summarized in Table.~\ref{tab:list_of_codes}.

\begin{table*}  %%% DATA TABLE %%%
\caption{List of photo-$z$ codes featured in this study. ML here means machine learning.} \label{tab:list_of_codes}\resizebox{\textwidth}{!}{
\begin{tabular}{llll}
\hline
\bf Code 			& \bf Type & \bf Paper & \bf Website \\
\hline
\textsc{BPz} 		& template 			& \citet{Benitez:00}		& \url{http://www.stsci.edu/~dcoe/BPZ/} \\
\textsc{EAZY} 		& template 			& \citet{Brammer:08}		& \url{https://github.com/gbrammer/eazy-photoz} \\
\textsc{LePhare} 	& template 			& \citet{Arnouts:99}		& \url{http://www.cfht.hawaii.edu/~arnouts/lephare.html} \\
\textsc{ANNz2} 		& ML 	& \citet{Sadeh:16}			& \url{https://github.com/IftachSadeh/ANNZ} \\
\textsc{Delight} 	& ML/template 	& \citet{Leistedt:17}		& \url{https://github.com/ixkael/Delight} \\
\multirow{ 2}{*}{\textsc{FlexZBoost}} & \multirow{ 2}{*}{ML} 	& \multirow{ 2}{*}{\citet{Izbicki:17}}		& \url{https://github.com/tpospisi/flexcode};\\ 
					& 		&							& \url{https://github.com/rizbicki/FlexCoDE}\\
%\textsc{Frankenz} 	& ML 	& \citet{Speagle:frankenz}	& \url{https://github.com/joshspeagle/frankenz} \\
\textsc{GPz} 		& ML	& \citet{Almosallam:15b}	& \url{https://github.com/OxfordML/GPz} \\
\textsc{METAPhoR} 	& ML 	& \citet{Cavuoti:17}		& \url{http://dame.dsf.unina.it}\\
\textsc{CMNN} 		& ML 	& \citet{Graham:17}			& - \\
\textsc{SkyNet} 	& ML 	& \citet{Graff:14}			& \url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/} \\
\textsc{TPZ} 		& ML 	& \citet{Carrasco_Kind:13}	& \url{https://github.com/mgckind/MLZ} \\
\hline
\trainz 	& N/A	& See Section~\ref{sec:method:trainz} & \\
\end{tabular}}
\end{table*}

%\red{The questions that must be answered for each code are\dots}
The questions that must be answered for each code are: what unique features are included in the specific implementation that influence the output $p(z)$.  What form of validation was performed with the training data, how were photometric uncertainties employed in the analysis, how were negative fluxes treated, what specific prior form was employed (for template based codes), or what specific machine learning architcture was used (for ML codes)? 
%\scc{which parameter (in a general meaning) have been used, which kind of validation has been performed (if any)}
\subsection{Template-based Approaches}
\label{sec:templatecodes}

\subsubsection{BPZ}
\label{sec:BPZ}
%(Sam Schmidt)

\textsc{BPZ}\footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}} \citep[Bayesian Photometric Redshift,][]{Benitez:00} is a template-based photo-$z$ code that compares the expected colors ($C$) calculated for a set of spectral energy distribution (SED) types/templates ($T$) to the observed colors to calculate the likelihood of observing colors at each redshift for each type, $p(C|z,T)$. The code employs an empirically determined Bayesian prior in apparent magnitude ($m_0$) and SED-type. Assuming that the SED-types are spanning and exclusive, we can determine the redshift posterior $p(z|C,m_0)$ by marginalizing over all SED-types with a simple sum \citep[Eq.~3 from][]{Benitez:00}:

\begin{equation} \label{eq:redshift_posterior}
p(z|C,m_0)\,\propto\, \sum_{T}p(z,T|m_0)\,p(C|z,T)
\end{equation}
\noindent where the first term on the right-hand side is the Bayesian prior and the second term is the traditional likelihood. The prior is assumed to have the form: $p(z,T|m_0)=p(T|m_0)\,p(z|T,m_0)$, i.e. it parameterizes the prior as an evolving type fraction with apparent magnitude, combined with a prior on the expected redshift probability distribution as a function of both apparent magnitude and SED-type.

In this paper we use \textsc{BPZ v 1.99.3}. The template set employed here is the set of $100$ discrete SEDs described in Section~\ref{sec:buzztemplates}
%, and the $129$ Brown SEDs for the Galacticus dataset. 
To keep the number of free parameters to a manageable level the SEDs in the training set are sorted by the rest-frame $u$-$g$ colour and split into three ``broad'' SED classes, equivalent to the \texttt{E}, \texttt{Sp} and \texttt{Im/SB} types in \citet{Benitez:00}. We assume the same functional form for the Bayesian priors as used by \citet{Benitez:00}, and utilize the training-set galaxies with known SED-type, redshift, and apparent magnitude to determine the type fractions and the best fit for the eleven free parameters of the prior. 
%For photo-$z$ point estimates we use the \texttt{Z\_B} output parameter. 
For galaxies with negative flux in a measured band, the placeholder value is replaced with an estimate one $\sigma$ detection limit in that particular band, i.~e.~a value close to the estimated sky noise threshold. 
The type-marginalized $p(z)$ is generated by setting the parameter \texttt{PROBS\_LITE=TRUE} in the \textsc{BPZ} parameter file.

\subsubsection{EAZY} \label{sec:eazy}
%(Rongpu Zhou)

\textsc{EAZY}\footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} is a template-based photo-$z$ code that includes several features that improve on the basic $\chi^2$ fit used in many template codes. It can fit the observed photometry with SEDs created from a linear combination of a set of templates at each redshift, and the best-fit SED is found by simultaneously fitting one, two or all of the templates by minimizing $\chi^2$. The minimized $\chi^2(z)$ is then combined with an apparent magnitude prior to obtain the posterior redshift probability distribution, although some argue that this is not the mathematically correct way of calculating the posteriors. \textsc{EAZY} can also account for the uncertainties in the templates by adding an empirically derived template error in quadrature as a function of redshift to the flux errors.

In this paper we use the all-templates mode, which fits the photometric data with a linear combination of the five basis templates. We employed the $5$ basis templates described in Section~\ref{sec:buzzard}, and set the template error to zero since these same templates were used to produce the simulated catalog photometry. %\red{The quality parameter \texttt{Qz} is...}
The likelihoods are calculated on a 200-point redshift grid spanning $0\leq z \leq 2$, and include the application of a type-independent apparent magnitude prior estimated from the training data.

\subsubsection{LePhare}\label{sec:lephare}
%(C\'ecile Roucelle, Eric Nuss, Johann Cohen-Tanugi)

\textsc{LePhare}\footnote{\url{http://www.cfht.hawaii.edu/~arnouts/lephare.html}}\citep[Photometric Analysis for Redshift Estimate,][]{Arnouts:99,Ilbert:06} is a photo-$z$ reconstruction code based on a $\chi^2$ template-fitting procedure. The observed colors are matched with the colours predicted from a set of spectral energy distribution (SED) which can be either synthetic or based on a semi-empirical approach. \textsc{LePhare} has been used to produce the COSMOS2015 photo-$z$ catalogue \citep{Laigle:16}.

Each SED is redshifted in steps of $\Delta z = 0.01$ and convolved with the simulated LSST filter transmission curves (accounting for instrument efficiency). The opacity of the inter-galactic medium has been set to zero as no additional reddening has been included in the Buzzard simulations. The computed photo-$z$ is then the value that minimizes the merit function $\chi^2 (z,T,A)$ from \citet{Arnouts:99}:

>>>>

\RequirePackage[switch, columnwise, running, mathlines, displaymath,
mathlines]{lineno}
\RequirePackage{docswitch}
% \flag is set by the user, through the makefile:
%    make note
%    make apj
% etc.
\setjournal{\flag}

\documentclass[\docopts]{\docclass}

\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
  \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
  \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
  \renewenvironment{#1}%
     {\linenomath\csname old#1\endcsname}%
     {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
  \patchAmsMathEnvironmentForLineno{#1}%
  \patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

% You could also define the document class directly
%\documentclass[]{emulateapj}

% Custom commands from LSST DESC, see texmf/styles/lsstdesc_macros.sty
\usepackage{lsstdesc_macros}
% \usepackage{natbib}
% \usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{amsmath}
\usepackage{amsfonts}
\graphicspath{{./}{./figures/}}
\bibliographystyle{mnras}%mn2e

% Add your own macros here:

\newcommand{\lsst}{\textsc{LSST}}
\newcommand{\lsstdesc}{\lsst\textsc{-DESC}}
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{\pz\ PDF}% can easily change this to specify posterior throughout

@@

\def\X{{\mathbf{X}}}
\def\x{{\mathbf{x}}}
\def\E{{\mathbb{E}}}

% ======================================================================

\begin{document}
\linenumbers

\title{An assessment of photometric redshift PDF performance in the context of LSST}
% \title{Photometric redshift uncertainties for LSST \romannumeral{1}: A unified methodology for assessing photo-$z$ PDF performance}

\maketitlepre

\begin{abstract}

  Photometric redshift (photo-$z$) probability distribution functions (PDFs) are a key data product of nearly all upcoming galaxy imaging surveys.
  However, the photo-$z$ PDFs resulting from different techniques are not in general consistent with one another, and an optimal method for obtaining an accurate PDF remains unclear.
  We present the results of an initial study of the Large Synoptic Survey Telescope Dark Energy Science Collaboration (\textsc{LSST-DESC}), the first in a planned series of papers testing multiple photo-$z$ codes on simulations of upcoming LSST galaxy photometry catalogues.
  This initial test evaluates photo-$z$ algorithms in the presence of representative training data and in the absence of several common sources of systematic errors that affect the procedures by which photo-$z$ PDFs are derived.
  The photo-$z$ PDFs are evaluated using multiple metrics including the Kolmogorov-Smirnoff statistic, Cramer-von Mises statistic, Anderson-Darling statistic, Kullback-Leibler divergence, $N(z)$ moments, quantile-quantile plots and probability integral transform.
  We observe several trends, including an overall over/under-prediction in the broadness of the PDFs for several of the codes.
  A careful accounting of all systematics discovered will be necessary for the codes employed in upcoming analyses in order to achieve unbiased cosmological measurements.
  % Photometric redshift (photo-$z$) probability distribution functions (PDFs) more completely capture the complex nature of photo-$z$ uncertainties and are thus a key data product of nearly all upcoming galaxy imaging surveys, including the Large Synoptic Survey Telescope (LSST).
  % Photo-$z$ PDFs produced by different algorithms do not in general agree with one another, and no one technique has yet been identified as optimal, leading to a proliferation of photo-$z$ PDF estimation codes.
  % We present a unified comparison of twelve such codes using simulated LSST photometry, the first in a series of papers on photo-$z$ PDF performance for the LSST Dark Energy Science Collaboration (DESC).
  % In this initial study, we isolate the effects of the estimation procedure by running each code using perfectly representative training data (for machine learning methods) or the true SED template library (for template-fitting methods) and confirm the mutual inconsistency of the resulting photo-$z$ PDF estimates.
  % We apply a comprehensive suite of metrics to an the population of photo-$z$ PDFs as well as point estimates derived thereof and an accepted estimator of the redshift distribution $N(z)$.
  % % The photo-$z$ PDFs are evaluated using multiple metrics including the Kolmogorov-Smirnoff statistic, Cramer-von Mises statistic, Anderson-Darling statistic, Kullback-Leibler divergence, $N(z)$ moments, quantile-quantile plots, and probability integral transform.
  % We interpret the performance of the codes under each metric in terms of the assumptions underlying the overall approach of the methods and audit the sentivity of the metrics to the failure modes of different techniques, culminating in a discussion predicting the impact of introducing realistic systematics and the direction of attention to the choice of metric when identifying the most appropriate code for a given science use case.

\end{abstract}

% Keywords are ignored in the LSST DESC Note style:
\dockeys{galaxies: distances and redshifts -- galaxies: statistics -- methods: statistical}

\maketitlepost

% ----------------------------------------------------------------------
% {% raw %}

\input{./tex/introduction}

\input{./tex/data}

\input{./tex/methods}

\input{./tex/analysis}

\input{./tex/results}

\input{./tex/discussion}

\input{./tex/conclusion}

% ----------------------------------------------------------------------

\subsection*{Acknowledgments}

%%% Here is where you should add your specific acknowledgments, remembering that some standard thanks will be added via the \code{desc-tex/ack/*.tex} and \code{contributions.tex} files.

%This paper has undergone internal review in the LSST Dark Energy Science Collaboration. % REQUIRED if true

\input{contributions} % Standard papers only: author contribution statements. For examples, see http://blogs.nature.com/nautilus/2007/11/post_12.html

% This work used TBD kindly provided by Not-A-DESC Member and benefitted from comments by Another Non-DESC person.

% Standard papers only: A.B.C. acknowledges support from grant 1234 from ...

The authors would like to thank their LSST-DESC publication review committee.

AIM is advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.

\input{desc-tex/ack/standard} % also available: key standard_short

% This work used some telescope which is operated/funded by some agency or consortium or foundation ...

% The DESC acknowledges ongoing support from the Institut National de Physique Nucleaire et de Physique des Particules in France; the Science \& Technology Facilities Council in the United Kingdom; and the Department of Energy, the National Science Foundation, and the LSST Corporation in the United States.
%
% DESC uses resources of the IN2P3 Computing Center (CC-IN2P3--Lyon/Villeurbanne - France) funded by the Centre National de la Recherche Scientifique; the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231; STFC DiRAC HPC Facilities, funded by UK BIS National E-infrastructure capital grants; and the UK particle physics grid, supported by the GridPP Collaboration.
%
% This work was performed in part under DOE Contract DE-AC02-76SF00515.

% We acknowledge the use of An-External-Tool-like-NED-or-ADS.

%{\it Facilities:} \facility{LSST}

\input{./tex/appendix}

% Include both collaboration papers and external citations:
\bibliography{main,lsstdesc}

\end{document}

% ======================================================================
